---
title: "Introduction to wordler"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to wordler}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package lets you play a version of the [WORDLE game](https://www.powerlanguage.co.uk/wordle/) in R. You can either play interactively in the console, or programmatically to explore different solvers (for example).

# Load the package

First, load the package.

```{r setup}
library(wordler)
```

# Playing a game in the console

To play a game in the console, call the `play_wordler()` function.

```{r}
# Commented out so vignette can be generated
#play_wordler()
```

# Playing a game programatically

## Initialise a new game

First, initialise a new game.

```{r}
game <- make_new_game()
```

This returns a list which represents the game state. We'll have a look at the items in this list after we've made a few guesses.

## Make a guess

Use `have_a_guess()` to submit a guess of the target word. We'll make a few guesses below.

```{r}
game <- have_a_guess("SQUID", game)
game <- have_a_guess("VIDEO", game)
```

## Game state

Now let's look what's happening in the game object.

We have an item which represents whether the game is over, or still in play.

```{r}
game$game_over
```

This is set to `TRUE` if either the word is correctly guessed, or all guesses are used.

The `game_won` item indicates if the target word has been guessed correctly.

```{r}
game$game_won
```

The number of guesses made so far is held in the `guess_count` item.

```{r}
game$guess_count
```

The word we're trying to guess is held in the `target` item.

```{r}
game$target
```

The list of guesses so far is available in the `guess` item.

```{r}
game$guess
```

The `assess` item is a list holding the assessments of each guess.

```{r}
game$assess
```

At any time, we can print the status of the game as follows.

```{r}
print_game(game)
```

A vector of letters known to _not_ be in the target word is available.

```{r}
game$letters_known_not_in_word
```

A vector of letters known to be in the target word is available.

```{r}
game$letters_known_in_word
```

A vector of letters know to be in the right position in the target word is available.

```{r}
game$letters_known_in_position
```

